asc_file_database

### 2019-03-13 src/stack_test.Rmd
model tweaking

>>>>

testing model fiddling

```{r}
janpres <- read.csv("../output/bio/maxenttestjanpr.csv", header = TRUE)
janpres$occ <- 1
janab <- read.csv("../output/bio/maxenttestjanab.csv", header = TRUE)
janab$occ <- 0
prab <- rbind(janpres, janab)
prab$originalscientificname <- "cap" #because species name needs to be the same
pa <- prab$occ
prab <- subset(prab, select = -c(x, y, occ, originalscientificname)) #ok so for maxent in r just need the variables
prab
#write.csv(prab, "../output/bio/maxjan98test.csv", row.names = FALSE)

stacklist <- read.csv("../data/env/asc_layerlist1998.csv", header = TRUE)
stacklist <- subset(stacklist, stackname == "st199801000120")
stacklist[] <- lapply(stacklist, as.character)
stacklist
aea <- raster("../output/env/aea.tif")

temp_depth <- raster(stacklist$temp_depth)
crs(temp_depth) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
names(temp_depth) <- "temp_depth"
temp_depth <- projectRaster(temp_depth, aea)
chl_surface <- raster(stacklist$chl_surface)
crs(chl_surface) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
names(chl_surface) <- "chl_surface"
chl_surface <- projectRaster(chl_surface, aea)
o2_depth <- raster(stacklist$o2_depth)
crs(o2_depth) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
names(o2_depth) <- "o2_depth"
o2_depth <- projectRaster(o2_depth, aea)
salinity_depth <- raster(stacklist$salinity_depth)
crs(salinity_depth) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
names(salinity_depth) <- "salinity_depth"
salinity_depth <- projectRaster(salinity_depth, aea)
nao_sample <- raster(stacklist$nao_sample)
crs(nao_sample) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
names(nao_sample) <- "nao_sample"
nao_sample <- projectRaster(nao_sample, aea)
nao_winter <- raster(stacklist$nao_winter)
crs(nao_winter) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0"
names(nao_winter) <- "nao_winter"
nao_winter <- projectRaster(nao_winter, aea)

test <- stack(temp_depth, chl_surface, o2_depth, salinity_depth, nao_sample, nao_winter)

system.file("java", package="dismo") #finding location to put maxent jar file
system("java -version")

mod1 <- maxent(x = prab, p = pa, args=c("maximumiterations=5000")) #maxiterations increased to ensure model convergence
mod1

pre1 <- predict(mod1, test, args='outputformat=raw' ) 
preplot1 <- plot(pre1)
preplot1

pre2 <- predict(mod1, test, args='outputformat=logistic' ) 
preplot2 <- plot(pre2)
preplot2

pre3 <- predict(mod1, test, args='outputformat=cloglog' ) 
preplot3 <- plot(pre3)
preplot3

#------------------------

mod2 <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "defaultprevalence=0.8")) # changing the prev seems to do nothing
mod2

mod3 <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "defaultprevalence=0.1")) # changing the prev seems to do nothing
mod3

pre2.2 <- predict(mod2, test, args='outputformat=logistic' ) 
preplot2.2 <- plot(pre2.2)
preplot2.2

pre2.3 <- predict(mod3, test, args='outputformat=logistic' ) 
preplot2.3 <- plot(pre2.3)
preplot2.3

#-----------------------------

mod4 <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE")) 
mod4

mod5 <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "maximumbackground=100")) #because i am using swd, this command is overwridden.  
mod5

pre5 <- predict(mod5, test, args='outputformat=logistic' ) 
preplot5 <- plot(pre5)
preplot5
```
